Millions of Type Errors

### 2023-09-13 programming23/paper.tex
related: placeholder cite for liblit
add missing files, compass pdfs
checkpoint: start to programming-ize the abstract

\begin{abstract}
  {Roblox Studio} is a tool which places programming in the hands of
  millions of creators, ranging from high school students to professional
  development studios. It has the ability to report telemetry data,
  which allows large-scale measurement of the creator experience. In
  this paper, we discuss one use of telemetry, to measure the experience
  of type error reporting.
  We find FILL.

  %\let\paragraph\abstractpart

  % \paragraph{Context}
  %% What is the broad context of the work? What is
  %% the importance of the general research area?

  % \paragraph{Inquiry}
  %% What problem or question does the paper
  %% address? How has this problem or question been
  %% addressed by others (if at all)?

  %\paragraph{Approach}
  %% What was done that unveiled new knowledge?

  %\paragraph{Knowledge}
  %% What new facts were uncovered? If the
  %% research was not results oriented, what new
  %% capabilities are enabled by the work?

  %\paragraph{Grounding}
  %% What argument, feasibility proof, artifacts,
  %% or results and evaluation support this work?

  %\paragraph{Importance}
  %% Why does this work matter?

@@

TODO must show full plot, zoomed plot side by side

@@

\begin{figure}[t]\centering
TODO diff vs 1st, not previous

  % > is not a valid filename char on some OSs!
  \includegraphics[width=\columnwidth]{img/error-count-nocheck-row--te-density-diff.pdf}
  \includegraphics[width=\columnwidth]{img/error-count-nonstrict-row--te-density-diff.pdf}
  \includegraphics[width=\columnwidth]{img/error-count-strict-row--te-density-diff.pdf}

@@

\begin{figure}[t]\centering
  %% TODO
  %% - thin bars
  %% - colors for good , bad (disagree) , neutral
  \begin{tabular}{lll}
    \mnocheck{} & \mnonstrict{} & \mstrict{} \\
    % Missing file
    % \includegraphics[width=0.3\columnwidth]{img/compass-nocheck.pdf}
    &
    % Missing file
    % \includegraphics[width=0.3\columnwidth]{img/compass-nonstrict.pdf}
    &
    % Missing file
    % \includegraphics[width=0.3\columnwidth]{img/compass-strict.pdf}
  \end{tabular}
  \caption{FILL Are there fewer type errors than forcedstrict errors? Expect true always, but that is not the case.}
  \label{f:tefs}
\end{figure}

@@

>>>>

\begin{abstract}
  \let\paragraph\abstractpart

  \paragraph{Context}
  %% What is the broad context of the work? What is
  %% the importance of the general research area?
  {Roblox Studio} is a tool that lets millions of creators
  build interactive experiences by programming in a variant
  of Lua called Luau.
  The creators form a broad group, ranging from novices writing
  their first script to professional Luau developers, thus Luau
  must support a wide audience.
  As part of its efforts to support all kinds programmers, Luau includes a
  gradual type system that goes to great lengths to minimize false positive
  errors.

  \paragraph{Inquiry}
  %% What problem or question does the paper
  %% address? How has this problem or question been
  %% addressed by others (if at all)?
  Since Luau is in the hands of so many creators,
  how do they use it?
  Of central importance, however, is protecting the privacy
  of Luau creators.
  FILL

%  TYPE ERRORS
%  investigate

  It has the ability to report telemetry data,
  which allows large-scale measurement of the creator experience. In
  this paper, we discuss one use of telemetry, to measure the experience
  of type error reporting.
  We find FILL.

  \paragraph{Approach}
  %% What was done that unveiled new knowledge?
  FILL impersonal telemetry, N months.

  \paragraph{Knowledge}
  %% What new facts were uncovered? If the
  %% research was not results oriented, what new
  %% capabilities are enabled by the work?
  FILL

  \paragraph{Grounding}
  %% What argument, feasibility proof, artifacts,
  %% or results and evaluation support this work?
  Our findings are supported by a publicly-available dataset
  of over 1.5 million telemetry records.

  \paragraph{Importance}
  %% Why does this work matter?
  FILL improve Luau, offer lessons to similar developments (epic?, elixir?).

@@

@@

\begin{figure}[t]\centering
% TODO diff vs 1st, not previous

  \mnocheck{}
  \includegraphics[width=\columnwidth]{img/error-count-nocheck-row--te-density-diff.pdf}
  \medskip
  \mstrict{}
  \includegraphics[width=\columnwidth]{img/error-count-nonstrict-row--te-density-diff.pdf}
  \medskip
  \mstrict{}
  \includegraphics[width=\columnwidth]{img/error-count-strict-row--te-density-diff.pdf}

@@

\begin{figure}[t]\centering
  %% TODO
  %% - thin bars
  %% - colors for good , bad (disagree) , neutral
  \begin{tabular}{lll}
    \mnocheck{} & \mnonstrict{} & \mstrict{} \\
    \includegraphics[width=0.3\columnwidth]{img/compass-nocheck.pdf}
    &
    \includegraphics[width=0.3\columnwidth]{img/compass-nonstrict.pdf}
    &
    \includegraphics[width=0.3\columnwidth]{img/compass-strict.pdf}
  \end{tabular}
  \caption{FILL Are there fewer type errors than forcedstrict errors? Expect true always, but that is not the case.}
  \label{f:tefs}
\end{figure}

@@

Liblit dissertation~\cite{liblit-thesis}

RAMSS workshop series.
